A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-12-01 paper_review/response_1.txt

REVIEWER COMMENT
----------
Line 78 (Kepler ages): Consider adding citation to Walkowicz & Basri
(2013)

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Line 93: Clarify origin of name delta Lyr, given there are two
pre-existing names, and how they overlap. It might also be worth
mentioning Kerr's Cep-Her association as in prep just to save future
readers the headache of cross-identifying them, either here or in Sec
2.1

RESPONSE
----------
> delta Lyr cluster was the first name suggested by Stephenson
> (1958), and it is the default name listed in SIMBAD.  It was also
> the name used in the title of Eggen's 1967 paper.
>
> The cluster was called Stephenson-1 by people other than
> Stephenson, including by Kounkel & Covey 2019.  The Kounkel & Covey
> 2019 "Theia" catalog identifiers are simply given to any cluster in
> their catalog, in addition to any previous names that existed.
>
> The overlap between the earlier lists (Stephenson 1958, Eggen 1968,
> Kharchenko et al. 2012) and the Theia 73 list from Kounkel & Covey
> 2019 is only present in the stars closest to delta Lyr itself.  For
> instance, see the 30 stars shown in Figure 1 of Eggen 1968.  The
> broader "complex" shown in Figure 1 of our manuscript was to our
> knowledge first reported to be a set of kinematically associated
> stars by Kounkel & Covey -- inasmuch as an "HDBScan group" implies
> kinematic association.
>
> Regarding Ronan Kerr's view of the delta Lyr cluster as a component
> of the larger Cep-Her complex, we would prefer to leave this as
> Ronan's result to present!  There's significant work here in
> designing the clustering method and verifying that it works.
> There's also work in understanding the overall structure of the
> broader association (which is different in nuanced ways from the
> gray Theia 73 points in Figure 1).  Given the complexity, and the
> potential importance of the complex given its proximity and age, we
> really would prefer to leave this for the in prep R. Kerr work.
> And similarly, the introduction of the term "Cep-Her complex" is
> probably best left for that future work, where it can be mentioned
> that the "del Lyr cluster" is a subset of this complex.

@@

REVIEWER COMMENT
----------
Line 165: Consider mentioning the axes on which data was cleaned
(e.g. color precision)

RESPONSE
----------
> Done - thank you.  We have added the sentence: "This also involved
> cuts on the photometric signal to noise ratio, the number of
> visibility periods used, the astrometric $\chi^2$ of the
> single-source solution, and the $G_{\rm BP}-G_{\rm RP}$ color
> excess factor."

@@

REVIEWER COMMENT
----------
Line 179 (reddening): What does "reasonably well" mean? Something
like 1-2 sigma?

RESPONSE
----------
> Thank you for catching the imprecise wording.  The revised text now
> reads as follows: "These values are within a factor of two of
> previously reported values in the literature (citations), and are
> all small enough that the choice of whether to use them {\it vs.}
> other extinction estimates does not affect our primary
> conclusions."
>
> More quantitatively, from the Lallement maps we find
> $E(B-V)=\{0.084\pm0.041, 0.020\pm0.003, 0.045\pm0.008,
> 0.032\pm0.006\}$ for UCL, IC 2602, the Pleiades, and the delta Lyr
> cluster respectively.  The relevant literature reports:
>
>    Gaia+2018 E(B-V):
>    Pleiades 0.045
>    IC2602 0.031
>   
>    KC2019: E(B-V)
>    Pleiades 0.071
>    IC2602 0.078
>    del Lyr cluster 0.059
>   
>    Bossini+2019 E(B-V)
>    Pleiades/Melotte22 0.045
>    IC2602 0.031
>    del Lyr cluster 0.051
>
>    Randich+2018 E(B-V):
>    IC2602 0.032 - 0.092
>
>    Pecaut & Mamajek 2016 Table 7 UCL members E(B-V)
>    UCL 0.059
>
> hence our assessment of "it's within a factor of two, and doesn't
> matter much."  Given that all these clusters are within ~400
> parsecs, this perhaps isn't too surprising.

@@

REVIEWER COMMENT
----------
Fig 3: It may be helpful to include one of the even younger clusters
on the CMD (i.e. to bracket delta Lyra), though perhaps it makes the
plot too busy.

RESPONSE
----------
> Please see camd_with_UCL.png attached.  This does make the plot a
> bit too busy, in our opinion.

@@

REVIEWER COMMENT
----------
Page 3: Consider re-organizing. Based on the 1st paragraph, I thought
the quantitative analysis would only deal with Pleiades and IC 2602
and one might infer reddening was only calculated for these clusters
(whereas I assume the latter are also corrected for reddening prior
to the analysis described). My suggestion would be to introduce all
the clusters first. It would also be helpful to list the age of IC
2602 at some point in the text.

RESPONSE
----------
> Thank you for this suggestion.
>
> The first paragraph of Section 2.2.1 has been reorganized to now
> introduce all five of the relevant clusters: UCL, IC 2602, del Lyr
> cluster, mu-Tau, and the Pleaides.  The second paragraph has been
> modified to account for this hcnage.
>
> The extinction for UCL is now also listed in the text.  So is the
> adopted age of IC 2602.

@@

REVIEWER COMMENT
----------
Line 202 (binaries): Add RUWE citation(s). Nice approach to remove
radial_velocity_error based on each cluster's distribution. It should
be noted somewhere in this discussion that the target itself does
*not* meet the RUWE limit and so wouldn't appear on the plot by
default.

RESPONSE
----------
> We've added a footnote to the Gaia DPAC memo by Lindegren on the
> RUWE.
>
> The stars shown in Figure 3 are those discussed in the first
> paragraph of Section 2.2.1.  (The binarity cut has not yet been
> applied -- which is why the binary sequence is visible for the δ Lyr
> cluster).  So for the latter point, we have not made any changes.

REVIEWER COMMENT
----------
Line 209: I don't follow starting "assembled a piecewise grid of
hybrid isochrones..." What does "hybrid" mean here? Once the splines
for each cluster are defined, how does one interpolate between them?
Are the ages then determined for each star and combined?

RESPONSE
----------
> The manuscript relies on the citation to Gagne+2020 for the full
> description of this method.  The "hybrid" isochrone I_i is the
> linear combination of any two reference isochrones.  The cited
> Equation 6 of Gagne+2020's mu-Tau paper gives the definition:
>
>   I_i = α_i * I_45 + (1-α_i)*I_112,
>
> for α_i a coefficient between 0 and 1, I_45 the reference 45 Myr
> isochrone spline (from Tuc-Hr, Columba, and Carina in Gagne's
> paper), and I_112 the Pleiades isochrone spline. 
>
> In our case, given our different reference clusters, the definition
> is modified to
>
>   I_i = α_i * I_16 + (1-α_i)*I_38,   (age from 16-38 Myr)
>   I_i = α_i * I_38 + (1-α_i)*I_112,  (age from 38-112 Myr)
>
> where I_38 is the IC 2602 isochrone spline, and I_16 is the UCL
> isochrone spline.
>
> The main assumption of this approach is that between the reference
> times set by the adopted clusters, the isochrones evolve linearly
> in time through color-absolute magnitude space.  If we were to
> attempt this linear interpolation all the way from UCL to the
> Pleiades without putting any intermediate point, the validity of
> this assumption would be crucial to test.  Since we include IC
> 2602, and it overlaps almost directly on the CAMD with the δ Lyr
> cluster, the only useful quantity that this method really gives us
> is a formal uncertainty on the age.  (Since the age the method
> returns will be very close to whatever age we adopt for IC 2602).
>
> To better illustrate the method, we've attached a figure to the
> response, "age_interpolation_example.png". This shows the CAMD data
> from the clusters after all the cleaning steps, their reference
> splines (constructed from bins over a select color range), and the
> interpolated splines spaced every 4.4 Myr between UCL and IC2602,
> and every 14.8 Myr betwen IC2602 and Pleiades.  While we do
> interpolate over a much finer grid, this is not shown to improve
> the clarity of the figure.  The age of δ Lyr is determined by using
> all the stars in the displayed color range, through the referenced
> Equation 7 of Gange+2020, which is a Gaussian likelihood that
> treats the interpolated isochrone as the "model" and the δ Lyr
> cluster's isochrone as the "data".  The statistical uncertainty on
> the age is then the standard deviation of a Gaussian fit to the
> posterior probability (in log-age; it becomes asymmetric when
> transformed to linear age).  We've added a few sentences to the
> manuscript to clarify this latter point.

@@

REVIEWER COMMENT
----------
Line 230 (age): Consider adopting a systematic error (perhaps
corresponding to the range noted for the extremes of the ages) in
addition to the random (assumed to be the quoted +6/-5 error).
Relatedly, how are the quoted errors derived?

RESPONSE
----------
> We're comfortable quoting the statistical error derived from the
> standard deviation of the logarithmic age posterior since this
> distribution is roughly Gaussian (see the attached
> del_lyr_cluster_age_posterior.png).  The worry with quoting a
> systematic error, e.g., "The age of the δ Lyr cluster is
> $38^{+6}_{-5}$ (stat) $^{+6}_{-8}$ (sys)" is that the systematic
> uncertainties are not Gaussian and are not based on any probability
> distribution that we can easily assess -- they're estimated based
> on the extremes of previous literature age measurements.  Quoting
> this systematic range next to a number that has been derived based
> on a more formal approach (and that has statistical meaning within
> that approach) somehow misses the point.  Given the comparable
> amplitude of the two sources of uncertainty, does this matter?
> Discussing the range of extremes in the text does communicate the
> point that this is a source of systematic uncertainty.

@@

REVIEWER COMMENT
----------
Line 391: It would be helpful to state the star's RUWE in the text here.
Additionally, I believe RUWE acornym was already defined previously.

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Section 3.2: Comment on whether the binary companion should effect
the rotation measurement of the host star (either here, or in the
rotation section).

RESPONSE
----------
> We've added the following sentence at the beginning of Section 4.1,
> when the Kepler light curve is introduced
>
> """
> The resulting photometry is dominated by a quasi-periodic starspot
> signal with a peak-to-peak amplitude that varies between 2\% and 8\%.
> \added{Given that the secondary companion's brightness in the Kepler
> band is 1\% to 2\% that of the primary, source confusion for the
> rotation signal is not expected to be an issue.}
  """
> The rationale here is that the rotation amplitude on the secondary
> would need to be a factor of >two times its intrinsic brightness for
> any confusion to happen, and the primary would need to not show any
> rotation signal.  Such large variability amplitudes have not been
> observed except for disked stars (e.g., Rebull+2020, Figure 10), and
> there is no evidence for a secondary period in the Lomb Scargle
> periodograms.

@@

REVIEWER COMMENT
----------
One note about the transit analysis: The MuSCAT3 data was introduced
as supporting evidence but the conclusion (that the transits appear
achromatic) was never explicitly stated.

RESPONSE
----------
> Line 642 of the original manuscript notes "Although we did not
> detect the RM anomaly, the multi-band MuSCAT3 light curves show
> that the transit is achromatic (Figure 7)."  We have nonetheless
> reworded this section to improve the clarity with which this point
> is made.

@@

REVIEWER COMMENT
----------
Line 725: The fast rotation period and flares could plausibly effect
the completeness.

RESPONSE
----------
> These completeness statistics were computed using KeplerPORTS (the
> Burke & Catanzarite 2021 citation).  KeplerPORTS corrects for red
> noise in the light curves by using the CDPP over different
> timescales -- see Section 3.3 of Burke, C. J. & Catanzarite, J.
> 2017, Planet Detection Metrics: Per-Target Detection Contours for
> Data Release 25, KSCI-19111-002.  This correction is performed
> using both a) the slope of the RMS CDPP versus transit duration for
> for "long" transit durations (the average of 7.5, 9.0, 10.5, 12.0,
> 12.5, and 15.0 hours) and b) the same slope for "short" transit
> durations (2.0, 2.5, 3.0, 3.5, and 4.5 hours). We retrieved these
> values from the DR25 Kepler occurrence rate products hosted on the
> NASA Exoplanet Archive.  For Kepler 1627, they were CDPP_long =
> 0.25478 and CDPP_short=0.79505.  Per Figure 2 of the KSCI-19111-002
> memo, these do indeed indicate a noisy star -- no surprises.
>
> We've added a sentence to the manuscript to clarify that we are
> talking about per-target detection contours, which should correct
> for the impact of at least the fast rotation period, inasmuch as it
> manifests in the slope of the CDPP versus transit duration.  We
> have also modified the wording for clarity, and have added a
> citation to Burke & Catanzarite's 2017 KSCI-19111-002 memo.
>
> To determine whether this CDPP-based detection efficiency
> correction is accurate given the exact red-noise properties of
> Kepler-1627 (i.e., the rotation and flares), a full
> injection-recovery analysis of the light curve with a pipeline of
> our own would be necessary. This effort is outside our scope, for
> now.

@@

REVIEWER COMMENT
----------
Line 729: Considering Owen 2020, contraction could also contribute to
some extent to the larger radii of small planets; might this be
significant?

RESPONSE
----------
> Thank you for this point -- we've added a sentence in the
> discussion to mention this possibility.

@@

RESPONSE
----------
> Done, thank you.

******************************************
Reviewer #2:

REVIEWER COMMENT
----------
Abstract
line 24: Kepl-1627Ab cannot be a "mini-Neptune" if it is same size of
Neptune.  Replace with "Neptune-size" Yes, it falls within a
distribution of objects in a period-radius diagram with an average
that is smaller than Neptune, but claiming affiliation with smaller
objects implies more than we know about this planet, e.g. its mass.

RESPONSE
----------
> Point well-taken.  R_p = 3.82 +/- 0.16 R_earth, so yes, Kepler-1627
> Ab is the same size as Neptune within 1-sigma.  All instances in
> the text that referred to Kepler-1627 Ab as a mini-Neptune have
> been modified to call it a "Neptune-sized planet", including the
> manuscript's title.

@@

REVIEWER COMMENT
----------
line 25: Kepler target stars were chosen for their suitability for
transiting detection of planets in general, and for planets that are
Earth-analogs in paraticular. That involves radius, brightess.
Distance and spectral types were not direct selection criteria; this
was before Gaia.

RESPONSE
----------
> Indeed.  Batalha+2010 (ApJL) discuss the selection function, which
> favored stars that were both small and bright since these stars
> enable the detection of Earth-size planets.  M dwarfs thus were
> generally excluded unless they happened to be very close.  F, G,
> and K stars were favored, particularly when they were nearby.  The
> sentence in L25 currently states that "The star was observed by the
> Kepler space telescope because it is nearby (d=329pc) and it
> resembles the Sun".  More directly, yes, the star was chosen
> because it was thought that it might enable the detection of small
> planets in the habitable zone.  However the underlying reason for
> why the star enables such detections is based on the star's
> brightness and assumed radius, which both factor into the transit
> SNR.  Our claim therefore holds, albeit indirectly.  It also serves
> the more important purpose of informing the reader what kind of
> star this paper is about: a star that is at a distance of ~330
> parsecs, and that resembles the Sun (except for its age!).

@@

RESPONSE
----------
> Done here and throughout the manuscript, thank you.

REVIEWER COMMENT
----------
Intro

Line 47: (First paragraph on p 2) the time-scale of 1e8 is associated
with one particular set of photoevaporation models; core-powered mass
loss proposes timescales of Gyr(s) (see the Ginzburg paper that was
cited). More recent photoevaporation models also propose 1 Gyr
timescales. It would be good to revise/update this paragraph.

RESPONSE
----------
> The sentence corresponds to a claim that mini-Neptunes are
> "expected to shrink in size by factors of several over their first
> 10^8 years".   The Owen 2020 models are then cited because this is
> their main claim: e.g., Figure 1 top panel of Owen 2020.  The range
> in initial raddi from that study come from differences in
> assumptions about whether or not the boil-off phase (Owen & Wu
> 2016) happens, and differences in assumption about the envelope to
> core mass ratio.
>
> Nonetheless, the point is well-taken.  We've added a sentence that
> clarifies that the outflows are expected to persist for 1e8 to 1e9
> years, and have added citations to Gupta & Schlichting 2020, Rogers
> & Owen 2021, and King & Wheatley 2021.

@@

REVIEWER COMMENT
----------
Section 2

Line 65: it is convention to italicize names of space missions like
TESS and K2

RESPONSE
----------
> Yes, and we leave the imposition of this convention to the
> copy-editors at the journal.

@@

REVIEWER COMMENT
----------
Lines 142-144: perhaps rephrasing this would clarify that the authors
did not use Kepler-1627 as a fiducial star about which to select
cluster members, and that they restricted the analysis to one of
several sub-clusters or clumps which contained Kepler-1627.

RESPONSE
----------
> We have rephrased Lines 142-144 to clarify the meaning, which is
> indeed what the reviewer has stated.

@@

REVIEWER COMMENT
----------
Figure 1: the first three panels would be more effective if they were
plotted at the same scale and with appropriately aligned axes. As
such the upper right panels are too small to be useful. Consider
leaving out the Sun (which is irrelevant) so as to have a more
appropriate choice of scale to how the details of the cluster. The
purpose of the fourth panel (tangential velocities) and the second
line in the caption are unclear to me. Aren't the tangential
velocities known from Gaia proper motions and parallaxes? Why
calculate them with the assumption of common space motion? If that is
done, what does it show, anyway?

### 2021-12-01 paper/ms.tex
reviewer #1 complete; a few reviewer #2 items todo

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, \added{we }have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  \added{We
calculated the tangential velocities for each of these stars relative to \sn\
($\Delta \mu^{*}$) by subtracting the observed proper motion from what the proper motion at the star's
position would be if it were co-moving with \sn. }The reported
cluster members (gray and black points) extend over a much larger
volume \added{in both physical and kinematic space }than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.
\added{One reason to suspect this is that the spread in tangential
velocities exceeds typical limits for kinematic coherence
\citep{Meingast2021}}.
We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed
\replaced{the}{this}
selection cut\deleted{s} manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

@@

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and
the field.  The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of $E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}\added{,
and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.\added{ The latter photoevaporative and core-powered
	outflows are thought to persist for $\approx$$10^8$ to $\approx$$10^9$ years,
	though the details depend on the planetary masses,
	the irradiation environments, and the initial atmospheric
	mass fractions \citep{owen_evaporation_2017,gupta_signatures_2020,2021MNRAS.503.1526R,2021MNRAS.501L..28K}.} Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
\replaced{In Figure~\ref{fig:XYZvtang}, \added{we }have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20. }{For plotting purposes, we focused only
on the stars with parallax signal-to-noise exceeding 20.} \added{We
calculated the tangential velocities for each of these stars relative to \sn\
($\Delta \mu^{*}$) by subtracting the observed proper motion from what the proper motion at each star's
position would be if it were co-moving with \sn. }

\replaced{The}{Figure~\ref{fig:XYZvtang} shows that the} reported
cluster members (gray and black points) extend over a much larger
volume \added{in both physical and kinematic space }than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.
\added{One reason to suspect this is that the spread in tangential
velocities exceeds typical limits for kinematic coherence
\citep{Meingast2021}}.
We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed
\replaced{the}{this}
selection cut\deleted{s} manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

@@

We measured the isochrone age using an empirical approach.  The \added{upper }left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602\added{ ($\approx 38$\,Myr)}, the Pleiades\added{ ($\approx 115$\,Myr)}, and
the field. The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  
\added{We also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).
We adopted the UCL members from \citet{Damiani2019}.
For visual clarity, the latter two clusters are not shown in Figure~\ref{fig:age}.
}
We cleaned \replaced{these}{the membership lists}
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.

\replaced{We then corrected for extinction by querying}{To correct for extinction, we queried} the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For \added{UCL, }IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of \replaced{$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}{$E(B-V)=\{0.084\pm0.041, 0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \replaced{\citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}}{\citep{pecaut_star_2016,GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}}\added{,
and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  \replaced{In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}). The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.}{The
pre-main-sequence M dwarfs of the \cn\ were also seen to be ``below''
UCL and ``above'' the Pleiades.}  To turn this heuristic interpolation
into \replaced{an age}{a quantitative age}
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, \replaced{we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively}{we used UCL, IC\,2602, and the
Pleiades}.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{~6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}
